\documentclass[]{deedy-resume-openfont}
\usepackage{fancyhdr}
 
\pagestyle{fancy}
\fancyhf{}
 
\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     LAST UPDATED DATE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\lastupdated

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\namesection{Sarjana}{M.I.}{ \urlstyle{same}
+91 98925262246 | \href{mailto:sarjananaidu@gmail.com}{sarjananaidu@gmail.com}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.33\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education} 

\subsection{Panimalar Engg. College}
\descript{BE Computer Science Engineering}
\location{Jun 2022 | Chennai, India}
\location{ CGPA: 9.0 / 10.0 }
\sectionsep

\subsection{Balalok Matric Higher Secondary School}
\descript{Higher Secondary}
\location{May 2018 | Chennai, India}
\location{ CGPA: 9.2 / 10.0 }
\sectionsep

\subsection{Balalok Matric Higher Secondary School}
\descript{SSLC}
\location{May 2016 | Chennai, India}
\location{ CGPA: 9.87 / 10.0 }
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     LINKS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Links} 
Website: \href{https://sarjana-codes.vercel.app/}{\bf https://sarjana-codes.vercel.app/} \\
\vspace{\topsep}
LinkedIn:  \href{https://www.linkedin.com/in/sarjana-m-i-5a2203193/}{\bf https://www.linkedin.com/in/sarjana-m-i-5a2203193/} \\
\vspace{\topsep}
Instagram:  \href{https://www.instagram.com/sarjana_ik/}{\bf https://www.instagram.com/sarjana_ik}\\

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     COURSEWORK
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Languages}
\textbf{English} - Full professional proficiency - Read, Write, Speak. \\
\vspace{\topsep}
\textbf{Tamil} - Native or bilingual proficiency -  Read, Write, Speak. \\
\vspace{\topsep}
\textbf{Telugu} - Native or bilingual proficiency -  Speak \\
\vspace{\topsep}
\textbf{French} - Basic - Read, Write \\
\vspace{\topsep}
\textbf{Kannada} - Limited Working Proficiency - Speak \\

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Skills}
\subsection{Programming}
\textbullet{} Java \textbullet{} Shell \textbullet{} Python \textbullet{} JavaScript \\
\textbullet{} C Sharp \textbullet{} Dot Net \\
\textbullet{} CSS \textbullet{} HTML \textbullet{} React JS \\
\textbullet{} Linux \textbullet{} SQL
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage} 
\hfill
\begin{minipage}[t]{0.66\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Experience}
\runsubsection{HCL}
\descript{| Technical Manager }
\location{Mar 2024 - Present | Chennai, India | Hybrid}
\vspace{\topsep}
\descript{\textbf{Project} - Data Management and Analytics}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Overseeing project execution and ensuring timely delivery.
\item Coordinating with cross-functional teams for seamless project integration.
\item Implementing data management strategies and analytics solutions.
\end{tightemize}
\vspace{\topsep}
\runsubsection{HCL}
\descript{| Software Engineer }
\location{Jul 2022 - Mar 2024 | Chennai, India | Hybrid}
\vspace{\topsep}
\descript{\textbf{Project}: Chabot Application}
\textbf{Technologies:} JavaScript, React JS 
\begin{tightemize}
\item Developed and maintained chatbot functionalities.
\item Collaborated with UX/UI designers to enhance user experience.
\item Conducted code reviews and implemented best practices.
\end{tightemize}
\vspace{\topsep}
\descript{\textbf{Project}: Work-Force Management (Schedule Engine)}
\textbf{Technologies:} C Sharp, Dot NET Framework 
\begin{tightemize}
\item Developed scheduling engine modules.
\item Integrated various components to optimize workforce management.
\item Debugged and resolved complex technical issues.
\end{tightemize}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     RESEARCH
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Projects}
\vspace{\topsep}
\runsubsection{Food Waste Reduction App} \\
\vspace{\topsep}
This user-friendly app enables anyone to register themselves and can add food items or view the food items that have been added. The user needs to provide their name, phone numbers and delivery address. The details of the delivery will be regularly updated in the database then and there, so people who want to contribute can add the food items and those who want to make use of the food items can give their delivery address and make sure they delete the food item available in the list.  \\
\vspace{\topsep}
\runsubsection{Face mask recognition system using CNN} \\
\vspace{\topsep}
The suggested technique successfully recognises the face in the image or video and then determines whether or not it has a mask on it. 
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     PUBLICATIONS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Certification} 
\vspace{\topsep}
\begin{tightemize}
\item \textbf{Game Development using PYGAME} – Issued by GUVI on May 2020
\item \textbf{Android App Development} – Issued by Infoziant Systems Pvt.Ltd on Jun 2019
\end{tightemize}

\section{Presentations} 
\vspace{\topsep}
\begin{tightemize}
\item \textbf{Insulin Pump} - Conducted on March 2020 by Panimalar Engineering College.
\vspace{\topsep}
\item \textbf{Sensitive Skin based on Biomedical Engineering} - Conducted on March 2021 BY SRM Valliammai College.
\end{tightemize}
\end{minipage} 
\end{document}  \documentclass[]{article}
